Quantum Interval-Valued Probability: Measurement and Probability

### 2017-10-02 prop_iop.tex
prop_letter.tex \section{Gleason} Updating...
prop_letter.tex -> prop_iop.tex Move a concrete example...

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{0229}{\c{e}}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}
\usepackage{enumitem}
\usepackage{amstext}

@@

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[3] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}

@@

\begin{lemma}Given a Hilbert space with the set of all projectors\nb$\events$,
and an additive interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
For two mixed states\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$. Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, if $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.\end{example}

>>>>

\documentclass[12pt]{iopart}
\usepackage[ backend=biber]{biblatex}
\addbibresource{prop.bib}
\ExecuteBibliographyOptions{sorting=none,maxbibnames=10,doi=false,isbn=false,url=false}
\usepackage{fullpage}
\usepackage{cmap}
\usepackage[T1,T2A]{fontenc}
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{0229}{\c{e}}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{mathrsfs}
\usepackage{bbold}
\usepackage{wesa}
\usepackage{graphicx}
\usepackage{verbatim}
\usepackage{iopams}
\usepackage{setstack}
\usepackage{enumitem}
\usepackage{amstext}
\usepackage{array}
\usepackage{booktabs}
\usepackage{multirow}

@@

\usepackage{color}
\usepackage[usenames,dvipsnames]{xcolor}
\newcommand{\amr}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{green}{Amr says: #1}\end{minipage}}}
\newcommand{\yutsung}[1]{\fbox{\begin{minipage}{0.9\textwidth}\color{purple}{Yu-Tsung says: #1}\end{minipage}}}
\newcommand{\set}[2]{\ensuremath{\left\{ {#1}~\middle|~{#2}\right\} }}
\def\C{{\mathbb{C}}}
\newcommand{\coreBorn}{\ensuremath{\overline{\Hilb}}}
\newcommand{\mul}[1][]{\ensuremath{\mu^{\mathrm{L{#1}}}}}
\newcommand{\mur}[1][]{\ensuremath{\mu^{\mathrm{R{#1}}}}}
% https://tex.stackexchange.com/questions/345284/can-i-have-an-almost-non-breaking-space-in-latex
% Change non-breaking space to \nolinebreak[1] 
% Hence, it will not hyphenate too much surrounding words.
\newcommand{\nb}{\nolinebreak[3] }
\newcommand{\iotal}[1][]{\ensuremath{\iota^{\mathrm{L{#1}}}}}
\newcommand{\iotar}[1][]{\ensuremath{\iota^{\mathrm{R{#1}}}}}
\newcommand{\tfrac}[2]{\textstyle\frac{#1}{#2}}

@@

\begin{lemma}\label{thm:Finite-precision-Gleason}Given a Hilbert
space with the set of all projectors\nb$\events$, and an additive
interval-valued function\nb$\iota:\left[0,1\right]\rightarrow\mathscr{I}$
with the maximum length of intervals in $\mathscr{I}$ is $\delta$.
For two mixed states\nb$\rho$ and $\rho'$, if $\rho'\in\coreBorn\left(\iota\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le\delta$.\end{lemma}

@@

\begin{example}Given the additive interval-valued function\nb$\widehat{\iota}_{n}:\left[0,1\right]\rightarrow\widehat{\mathscr{I}}_{n}$,
the maximum length of intervals in $\widehat{\mathscr{I}}_{n}$ is
$1/n$. Therefore, for any totally mixed state\nb$\rho$ on a $d$-dimensional
Hilbert space, if $\rho'\in\coreBorn\left(\widehat{\iota}_{n}\circ\mu_{\rho}^{\mathrm{B}},\events\right)$,
then $\left\Vert \rho-\rho'\right\Vert \le1/n$.

For example, when $n=2$, two states~$\rho_{0}=\frac{1}{3}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{1}{3}\cdot\proj{2}$
and $\rho_{1}=\frac{7}{24}\cdot\proj{0}+\frac{1}{3}\cdot\proj{1}+\frac{3}{8}\cdot\proj{2}$
can induce two QIVPMs~$\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
and $\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$. Given
any projector $P$ in the minimal subspace of events containing $\proj{0}$,
$\proj{1}$, and $\proj{2}$, $\events_{C}$, the interval-valued
probability of the induced QIVPMs, $\widehat{\iota}_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$
and $\widehat{\iota}_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$,
can be computed straightforwardly in Table~\ref{tab:Compute-the-QIVPM}.
\begin{table}
\caption{\label{tab:Compute-the-QIVPM}Compute $\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
and $\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ based on
$\mu_{\rho_{0}}^{\mathrm{B}}$ and $\mu_{\rho_{1}}^{\mathrm{B}}$
on $\events_{C}$.}
\centering{}%
\begin{tabular}{ccccc}
\toprule 
\addlinespace
$P$ & $\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{\rho_{0}}^{\mathrm{B}}\left(P\right)\right)$ & $\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)$ & $\widehat{\iota}_{2}\left(\mu_{\rho_{1}}^{\mathrm{B}}\left(P\right)\right)$\tabularnewline\addlinespace
\midrule
\midrule 
\addlinespace
$\mathbb{0}$ & $0$ & $\imposs$ & $0$ & $\imposs$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{0}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{7}{24}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{1}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\proj{2}$ & $\frac{1}{3}$ & $\left[0,\frac{1}{2}\right]$ & $\frac{3}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{2}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{5}{8}$ & $\left[\tfrac{1}{4},\tfrac{3}{4}\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{1}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}-\proj{0}$ & $\frac{2}{3}$ & $\left[\frac{1}{2},1\right]$ & $\frac{17}{24}$ & $\left[\frac{1}{2},1\right]$\tabularnewline\addlinespace
\midrule 
\addlinespace
$\mathbb{1}$ & $1$ & $\necess$ & $1$ & $\necess$\tabularnewline\addlinespace
\bottomrule
\end{tabular}
\end{table}
Table~\ref{tab:Compute-the-QIVPM} shows that $\rho_{0}$ is consistent
with $\widehat{\iota}_{2}\circ\mu_{\rho_{1}}^{\mathrm{B}}$ and $\rho_{1}$
is consistent with $\widehat{\iota}_{2}\circ\mu_{\rho_{0}}^{\mathrm{B}}$
both on every projectors in $\events_{C}$. Indeed, they are consistent
with each other on every projectors in $\events$ that implies $\left\Vert \rho_{0}-\rho_{1}\right\Vert \le\frac{1}{2}$
by lemma~\ref{thm:Finite-precision-Gleason}. This is true because
the exact value of $\left\Vert \rho_{0}-\rho_{1}\right\Vert $ is
$\frac{1}{24}$~\cite{544199}.\end{example}
